Why Donors Donate?

### 2020-09-14 analysis/05_market_simulator.Rmd
Fixed beta_persona

                        "Yes (1)", 

@@

                        "Very little trust",
                        "Little trust",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (1)",

@@

                        "Rarely",
                        "At least once a month (1)",

@@

                        "Very little trust",
                        "Little trust",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust (2)",

@@

                        "At least once a month (2)", 

@@

                        "Yes (2)",

@@

                        "Rarely",
                        "More than once a month, less than once a year",
                        "At least once a month (3)",

@@

                        "Involved (1)",

@@

                        "Involved (2)",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member", 

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member (1)",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member (2)",

@@

                        "Inactive member",
                        "Active member",

@@

                        "Inactive member",
                        "Active member",

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree",),
         selected = "Strongly agree")

@@

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree",),
         selected = "Strongly agree")

@@

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree",),
         selected = "Strongly agree")

>>>>

                        "Does travel", 

@@

                        "Very little trust in polticial institutions",
                        "Little trust in polticial institutions",
                        "Nuetral trust in polticial institutions",
                        "Some trust in polticial institutions",
                        "A lot of trust in polticial institutions",
                        "Complete trust in polticial institutions",

@@

                        "Rarely attend services",
                        "Attend at least once a month",

@@

                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities",

@@

                        "Donate At least once a month", 

@@

                        "Have volunteered",

@@

                        "Rarely volunteer",
                        "Volunteer more than once a month, less than once a year",
                        "Volunteer at least once a month",

@@

                        "Personally involved",

@@

                        "Family involved",

@@

                        "Inactive church member",
                        "Active church member",

@@

                        "Inactive sports member",
                        "Active sports member", 

@@

                        "Inactive educational member",
                        "Active educational member",

@@

                        "Inactive union member",
                        "Active union member",

@@

                        "Inactive party member",
                        "Active party member",

@@

                        "Inactive environmental member",
                        "Active environmental member",

@@

                        "Inactive professional member",
                        "Active professional member",

@@

                        "Inactive humanitarian member",
                        "Active humanitarian member",

@@

                        "Inactive consumer member",
                        "Active sonsumer member",

@@

                        "Inactive other member",
                        "Active other member",

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree")

@@

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree")

@@

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree")
